Results

### 2021-07-08 Analysis/03_Summarise_results.Rmd
Update 03_Summarise_results.Rmd

"hypervolume_richness"    
"hypervolume_dispersion"  
"hypervolume_regularity"

>>>>

### Richness

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "hypervolume_richness", level.names = removals, col = cols, legend.pos = "bottomright")
```

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "hypervolume_dispersion", level.names = removals, col = cols, legend.pos = "bottomright")
```

### Regularity

```{r, fig.height = 4, fig.width = 12}
plot.results(all_results, metric = "hypervolume_regularity", level.names = removals, col = cols)
```
